The interactions of rational, pragmatic agents\\ lead to efficient language structure and use

### 2019-02-02 paper/paper.tex
MF last changes and spell-checking.

Zipf articulated what is now considered a \emph{functionalist} approach
to language science -- analyzing language structure and use in terms of
efficiency. Such an approach might reframe our opening question as
follows: how does having property \textit{x} make using language
\(\ell\) more or less useful for communication? Among others, this
efficiency-based framing has produced a rich set of theoretical and
empirical targets exploring semantic typology (Regier, Kemp, \& Kay,
2015), properties such as ambiguity (Piantadosi, Tily, \& Gibson, 2011)
and compositionality (Kirby, Griffiths, \& Smith, 2014), and the
efficient use of reduction and redundancy in production (Genzel \&
Charniak, 2002; Levy \& Jaeger, 2007).\par

The approaches above typically posit efficiency measures motivated by
information-theoretic principles, but not directly grounded in language
use by interacting agents. In this work, we derive a measure of
efficiency from first principles of \textit{efficient language use} and
show how this can lead to communicatively efficient systems. We also
demonstrate that assumptions about interlocutors impact how language
properties are used efficiently. In this way, we bridge questions of
design and use in a single framework.\par

Functionalist theories commonly frame language efficiency in terms of a
fundamental effort-assymetry underlying everyday communication: what is
``hard'' for a speaker is likely different than what is ``hard'' for a
listener. Zipf described this as follows -- purely from the standpoint
of speaker effort, an optimal language \(\ell_{speaker}^*\) would tend
toward a vocabulary of a single, low-cost word. Given such a language,
the full set of potential meanings would be conveyed using only that
word, i.e. \(\ell_{speaker}^*\) would be fully ambiguous and all
possible meanings would need to be disambiguated by a listener. From the
standpoint of listener effort, an optimal language \(\ell_{listener}^*\)
would map all possible meanings to distinct words, removing a listener's
need to disambiguate. In this example, speaker effort is related to
\emph{production cost} and listener effort to \emph{understanding or
disambiguation cost}. Clearly, natural languages fall between the two
extremes of \(\ell_{speaker}^*\) and \(\ell_{listener}^*\). Zipf
proposed that the particular lexicon-level properties he observed were a
result of these competing forces -- the pressure to jointly minimize
speaker and listener effort.\par

@@

Adopting reference games as a basic unit of analysis suggests that
optimization may take place at the level of conversation. Importantly,
Zipf's conception of speaker and listener effort may be connected to how
language is used; in particular, whether interlocutors engage in
pragmatic reasoning during conversation. Under a Gricean treatment of
pragmatics, speakers and listeners follow a set of conversational maxims
in which they cooperate to transfer information (Grice, 1975). These
maxims appear to emerge from efficiency concerns, however (Horn, 1984).
We formalize this connection -- showing how system-level efficiencies
can emerge from local interaction behavior of pragmatic agents. Our
claim is that to understand an ``efficient'' property of a system it is
essential that we consider how that property is \emph{used}
efficiently.\par

We provide a case study for this approach, in which functionalist
regularities emerge from the dynamics of pragmatic communication. We
choose a property of languages that could, in principle, vary freely,
but shows strong regularities across languages. The explanadum is why
this regularity holds. We examine ambiguity as our property, extending
ideas by Piantadosi et al. (2011). We define a novel measure of
efficiency that depends on the interactional behavior of speaker and
listener agents. We adopt the reference game as our primary unit of
interaction and model language users with the Rational Speech Act (RSA)
framework -- a computional model of language use, which is nicely
attested by experimental data on interaction. Using these ingredients,
we show that the property of interest (ambiguity) is prevalent in
languages that optimize our measure of efficiency (Simulation 1).
Further, we show how ambiguity is used efficiently during local,
in-the-moment interactions (Simulation 2). Put differently, these
simulations examine efficiency from two angles -- in the first we vary
languages, fixing agents, and search for efficient designs. In the
second we vary agents, fixing language, and examine efficient use. \par

@@

Zipf's example of optimal speaker- and listener-languages took the form
of a reference game. We adopt that formulation here, assuming these
communication games as our basic unit of analysis. In this framework,
speakers and listeners are aware of a set of objects \(M\)
(\emph{meanings}) and are knowledgeable about the set of possible
signals \(U\) (\emph{utterances}) that can be used to refer to a given
meaning (see Figure 1). Utterances may have different relative costs,
operationalized via a prior over utterances \(P(U)\). Similarly,
meanings differ in the relative degree to which they need to be talked
about, operationalized as a prior over meanings
\(P(M)\)\footnote{The prior over meanings are analogous to the \textit{need probabilities} assumed in previous work (Regier, Kemp \& Kay (2015).}.
We consider a set of contexts \(C\) with an associated prior \(P(C)\).
Each context \(c\in C\) describes a different distribution over meanings
e.g. \(p(M|C=c_i) \neq p(M|C=c_j)\). Finally, we consider a set of
communicative events \(e \in E\) where \(<u, m, c> = e\) is an
utterance-meaning-context triple.\par

@@

A language \(\ell\) defines the set of semantic mappings between
utterances and meanings. For example, Figure 1 contains four utterances
\(U = \{\text{"blue"}, \text{"green"}, \text{"square"}, \text{"circle"}\} \text{ and three meanings }M = \{\text{green-square}, \text{blue-square}, \text{green-circle}\}\).
The boolean matrix describes the literal semantics of the language. We
define a language as ``ambiguous'' if there is some utterance
\(u \in U\) which can apply to multiple meanings (i.e.
\(|[[u_i]]| > 1\))\footnote{We use double brackets $[[\dots]]$ to represent denotation.}.
In Figure 1 both the words ``square'' and ``green'' are ambigous so we
would say that \(\ell\) contains ambiguity.

@@

The Rational Speech Act framework (RSA) is a computational-level theory
of pragmatic language use, which has produced good fit to human
communication behavior across a range of language phenomena (Frank \&
Goodman, 2012; Goodman \& Frank, 2016). RSA is a formalization of
essential Gricean pragmatic principles -- agents reason about one
another and their shared context (Grice, 1975). We adopt RSA as our
representational framework to model Gricean (rational and pragmatic)
speaker-listeners in the reference game setting (see
\href{https://github.com/benpeloquin7/zipf_principles/blob/master/paper/supplementary_materials.pdf}{SI}
and Goodman \& Frank (2016) for a review).\par

@@

We assume that speaker effort is related to the surprisal of an
utterance in a particular
context\footnote{In the current set of simulations we consider utterances costs as independent from context (ie. $p(u|c)p(c)=p(u)p(c)$).}
-- intuitively, the number of bits needed to encode the utterance \(u\).
This particular formalization of speaker-cost is general enough to
accommodate a range of cost instantiations, such as production
difficulty via articulation effort, cognitive effort related to lexical
access, or others (Bennett \& Goodman, 2018).\par

@@

Importantly, we assume that events \(e = <u, m, c>\) are sampled
according the to following generative model -- some context occurs in
the world with probability \(P(C=c)\). Within this context, an object
\(m\) occurs with probability \(p(m|c)\). The speaker attempts to refer
to that object by sampling from her conditional distribution
\(S(u|m, c; \ell)\) (i.e. \(e \sim p(c)p(m|c)S(u|m, c; \ell)\)). From
these ingredients it is possible to derive the following objective
between the speaker and listener distributions (see
\href{https://github.com/benpeloquin7/zipf_principles/blob/master/paper/supplementary_materials.pdf}{SI 2.1}
for complete derivation).

@@

\caption[Panel (A) Vertical axis shows the proportion of optimal languages containing ambiguity]{Panel (A) Vertical axis shows the proportion of optimal languages containing ambiguity. Horizontal axis shows the context-size (1-4) in each condition. Optimal language under CE objective (red). Speaker-optimal (blue). Listener-optimal (green). Error bars represent 95 percent confidence intervals. Panel (B), example CE-optimal language (ambiguous) under in a four-condition context. Panel (C), example CE-optimal language (unambiguous) in a single-condition context.}\label{fig:plot-optimal-langs}
\end{figure*}
\end{CodeChunk}

@@

For comparison, we also examine properties of optimal languages under
two additional objectives. Zipf (1949) proposed that the speaker-optimal
language \(\ell_{speaker}^*\) would minimize speaker effort and the
listener-optimal language \(\ell_{listener}^*\) would minimize listener
effort. We define these objectives using the first and second half of
equation 1 (see
\href{https://github.com/benpeloquin7/zipf_principles/blob/master/paper/supplementary_materials.pdf}{SI 2.2.}).\par

@@

Imagine a scenario in which a reader is beginning a news article. While
they may have some knowledge about the article's topic (perhaps from the
title), they may not have complete knowledge of its contents, including
the persons or events involved. In this setting, using a low-cost, but
ambiguous referring expression (say a pronoun like ``he'') early may
lead to misunderstanding if context is not informative. But, if by a
later position enough contextual information has accumulated, it may be
efficient to use the ambiguous expression. We pursue this general
framework in Simulation 2 -- examining when in a discourse using
ambigity is efficient. Note that we will consider ``context'' as
analogous to a ``topic'' of conversation. \par

@@

We conduct \(N=600\) simulations, generating discourses of length
\(|D|=30\) utterances, comparing three speaker models (\(n=200\) each).
We consider a single language
\(\ell\)\footnote{See SI for the matrix notation of this langauge.} with
\(|U|=6\) and \(|M|=4\) in which two of the utterances are ambiguous and
lower cost than the unambiguous utterances. (Note that use of this
particular language is not essential -- the results are broadly
generalizable to languages that contain ambiguity, but exploring this
space is computationally expensive.)\par

@@

We vary the degree to which agents can use context for disambiguation.
We consider three types of speaker models. Our \textit{Full pragmatics}
agent, models a speaker who reasons about her listener and also has
complete recall of the set of utterances in the discourse \(D\). This
speaker believes that the listener may not know the current topic
\(c_{current}\) at the start of the discourse, but can infer it over the
discourse. We compare two baseline models. The first, a
\textit{Partial pragmatics} baseline describes a speaker who reasons
about a listener, but assumes they have no access to the discourse
history. The second, a \textit{No pragmatics} baseline speaker does not
consider a listener at all, but produces utterances according to the
underlying langauge semantics (\(\ell\)) and topic probabilities
(\(p(M|C=c_{current}\)) (see
\href{https://github.com/benpeloquin7/zipf_principles/blob/master/paper/supplementary_materials.pdf}{SI 3}).\par

@@

Figure 3, panel (A) shows the empirical probability a speaker uses an
ambiguous utterance as a function of discourse position. The
\textit{No pragmatic} baseline uses ambiguous utterances frequently and
at a constant rate over the discourse. The \textit{Partial pragmatic}
baseline avoids ambiguous utterances entirely. But, the
\textit{Full pragmatic} model avoids ambiguous material only at the
start of the discourse, employing it increasingly as the discourse
proceeds. Panel (C) tracks our CE objective for each model over the
discourse. Note that the objective decreases for all three models,
primarily driven by the listener updating his belief about the actual
topic (\(P(C=c_{current}|D)\)). However, the objective declines more
quickly under the \textit{Full} and \textit{Partial pragmatic} speakers
as listener agents are better able to infer the correct context.
Additionally, the difference in CE between the \textit{Full}- and
\textit{Partial pragmatic} models at the end of the discourse is driven
by the reduction in speaker costs. Panel (B) tracks speaker effort,
which remains constant in both \textit{No pragmatic} and
\textit{Partial pragmatic} baselines. But, effort declines in the
\textit{Full pragmatic} model as she increasingly relies on ambiguous
material later in the discourse.\par

@@

How do the competing pressures of speakers and listeners give rise to
the distributional regularities found in natural language? Zipf (1949)
proposed that the asymmetry between speaker and listener costs gives
rise to a range of properties at the level of the lexicon. We explored
the interactions of rational pragmatic agents as a framework for
understanding efficient language structure and use. We focused on an
argument on the communicative function of ambiguity (Piantadosi et al.,
2011), deriving a novel speaker-listener Cross-Entropy objective for
measuring the efficiency of linguistic systems from first principles of
efficient language use. In Simulation 1 we showed that optimal languages
are more likely to contain ambiguous material when context is
informative. In Simulation 2 we showed how rational pragmatic agents use
ambiguous material efficiently in conversation.\par

A limitation of the current work is an analysis of exactly how the CE
objective compares to existing measures. For example, previous work has
described competing speaker-listener pressures in terms of a trade-off
of simplicity and informativeness (Kemp \& Regier, 2012) or expressivity
and compressibility (Smith, Tamariz, \& Kirby, 2013) to explain
linguistic regularities. Future work should assess the degree to which
we can derive the same properties as previous studies using our current
framework. In line with this idea, a primary focus of the current work
is to provide a case-study on the productivity of assessing
functionalist theories in repeated reference games between rational
pragmatic agents. We hope this framework can serve as a domain general
tool to assess the range of functionalist theories examining efficient
language-structure and use.\par

@@

\fbox{\parbox[b][][c]{7.3cm}{\centering {Code and SI: \href{https://bit.ly/2DOnjI4}{\url{https://bit.ly/2DOnjI4}}.}}}
\vspace{1em} \noindent

@@

\hypertarget{ref-RegierKempKay2015a}{}
Regier, T., Kemp, C., \& Kay, P. (2015). Word meanings across languages
support efficient communication. In B. M. \& W. O'Grady (Ed.), \emph{The
ahndbook of language emergence (pp. 237-263)}. Hoboken, NJ:
Wiley-Blackwell.

>>>>

Zipf articulated what is now considered a \emph{functionalist} approach
to language science -- analyzing language structure and use in terms of
efficiency. Such an approach might re-frame our opening question as
follows: how does having property \textit{x} make using language
\(\ell\) more or less useful for communication? This efficiency-based
framing has produced a rich set of theoretical and empirical targets
exploring semantic typology (Regier, Kemp, \& Kay, 2015), properties
such as ambiguity (Piantadosi, Tily, \& Gibson, 2011) and
compositionality (Kirby, Griffiths, \& Smith, 2014), and the efficient
use of reduction and redundancy in production (Genzel \& Charniak, 2002;
Levy \& Jaeger, 2007).\par

The approaches above typically posit efficiency measures that are
motivated by information-theoretic principles, but they typically do not
ground out in language use by interacting agents. In this work, we
derive an novel objective function from first principles of
\textit{rational language use} and show how optimizing this objective
can lead to communicatively efficient systems. We also demonstrate that
assumptions about interlocutors impact whether language properties are
used efficiently. In this way, we integrate questions of language design
and language use in a single framework.\par

Functionalist theories commonly frame language efficiency in terms of a
fundamental effort-asymmetry underlying everyday communication: what is
``hard'' for a speaker is likely different than what is ``hard'' for a
listener. Zipf described this as follows: purely from the standpoint of
speaker effort, an optimal language \(\ell_{speaker}^*\) would tend
toward a vocabulary of a single, low-cost word. Given such a language,
the full set of potential meanings would be conveyed using only that
word, i.e. \(\ell_{speaker}^*\) would be fully ambiguous and all
possible meanings would need to be disambiguated by a listener. From the
standpoint of listener effort, an optimal language \(\ell_{listener}^*\)
would map all possible meanings to distinct words, removing a listener's
need to disambiguate. In this example, speaker effort is related to
\emph{production cost} and listener effort to \emph{understanding or
disambiguation cost}. Clearly, natural languages fall between the two
extremes of \(\ell_{speaker}^*\) and \(\ell_{listener}^*\). Zipf
proposed that the particular lexicon-level properties he observed were a
result of optimization based on these competing forces -- the pressure
to jointly minimize speaker and listener effort.\par

@@

Adopting reference games as a basic unit of analysis suggests that
optimization may take place at the level of conversation. Importantly,
Zipf's conception of speaker and listener effort should be connected to
how language is used; in particular, whether interlocutors engage in
pragmatic reasoning during conversation. Under a Gricean treatment of
pragmatics, speakers and listeners follow a set of conversational maxims
in which they cooperate to transfer information (Grice, 1975). These
maxims appear to emerge from efficiency concerns, however (Horn, 1984).
We formalize this connection -- showing how system-level efficiencies
can emerge from local interaction behavior of pragmatic agents. Our
claim is that to understand an ``efficient'' property of a system it is
essential that we consider how that property is \emph{used}
efficiently.\par

We provide a case study for this approach, in which functionalist
regularities emerge from the dynamics of pragmatic communication. We
choose a property of languages that could, in principle, vary freely,
but shows strong regularities across languages. The explanandum is why
this regularity holds. We examine ambiguity as our property, extending
ideas by Piantadosi et al. (2011). We define a novel measure of
efficiency that depends on the interactional behavior of speaker and
listener agents. We adopt the reference game as our primary unit of
interaction and model language users with the Rational Speech Act (RSA)
framework -- a computational model of language use, which is supported
by experimental data on interaction. Using these ingredients, we show
that the property of interest (ambiguity) is prevalent in languages that
optimize our measure of efficiency (Simulation 1). Further, we show how
ambiguity is used efficiently during local, in-the-moment interactions
(Simulation 2). Put differently, these simulations examine efficiency
from two angles -- in the first we vary languages, fixing agents, and
search for efficient language designs. In the second we vary agents,
fixing language, and examine efficient use. \par

@@

Zipf's example of optimal speaker- and listener-languages took the form
of a reference game. We adopt that formulation here, assuming these
communication games as our basic unit of analysis. In this framework,
speakers and listeners are aware of a set of objects \(M\)
(\emph{meanings}) and are knowledgeable about the set of possible
signals \(U\) (\emph{utterances}) that can be used to refer to a given
meaning (see Figure 1). Utterances may have different relative costs,
operationalized via a prior over utterances \(P(U)\). Similarly,
meanings differ in the relative degree to which they need to be talked
about, operationalized as a prior over meanings
\(P(M)\)\footnote{The prior over meanings is equivalent to the \textit{need probabilities} assumed in previous work (Regier, Kemp \& Kay (2015).}.
We consider a set of contexts \(C\) with an associated prior \(P(C)\).
Each context \(c\in C\) describes a different distribution over meanings
e.g. \(p(M|C=c_i) \neq p(M|C=c_j)\). Finally, we consider a set of
communicative events \(e \in E\) where \(<u, m, c> = e\) is an
utterance-meaning-context triple.\par

@@

A language \(\ell\) defines the set of semantic mappings between
utterances and meanings. For example, Figure 1 contains four utterances
\(U = \{\text{"blue"}, \text{"green"}, \text{"square"}, \text{"circle"}\} \text{ and three meanings }M = \{\text{green-square}, \text{blue-square}, \text{green-circle}\}\).
The boolean matrix describes the literal semantics of the language. We
define a language as ``ambiguous'' if there is some utterance
\(u \in U\) which can apply to multiple meanings (i.e.
\(|[[u_i]]| > 1\))\footnote{We use double brackets $[[\dots]]$ to represent denotation.}.
In Figure 1 both the words ``square'' and ``green'' are ambiguous so we
would say that \(\ell\) contains ambiguity.

@@

The Rational Speech Act framework (RSA) is a computational-level theory
of pragmatic language use, which has produced good fit to human
communication behavior across a range of language phenomena (Frank \&
Goodman, 2012; Goodman \& Frank, 2016). RSA is a formalization of
essential Gricean pragmatic principles -- agents reason about one
another and their shared context (Grice, 1975). We adopt RSA as our
representational framework to model Gricean (rational and pragmatic)
speaker-listeners in the reference game setting (see
\href{https://bit.ly/2RBSGcU}{SI}).\par

@@

We assume that speaker effort is related to the surprisal of an
utterance in a particular
context\footnote{In the current set of simulations we consider utterances costs as independent from context (i.e.. $p(u|c)p(c)=p(u)p(c)$).}
-- intuitively, the number of bits needed to encode the utterance \(u\).
This particular formalization of speaker-cost is general enough to
accommodate a range of cost instantiations, such as production
difficulty via articulation effort, cognitive effort related to lexical
access, or others (Bennett \& Goodman, 2018).\par

@@

Importantly, we assume that events \(e = <u, m, c>\) are sampled
according the to following generative model -- some context occurs in
the world with probability \(P(C=c)\). Within this context, an object
\(m\) occurs with probability \(p(m|c)\). The speaker attempts to refer
to that object by sampling from her conditional distribution
\(S(u|m, c; \ell)\) (i.e. \(e \sim p(c)p(m|c)S(u|m, c; \ell)\)). From
these ingredients it is possible to derive the following objective
between the speaker and listener distributions (see
\href{https://bit.ly/2RBSGcU}{SI 2.1} for complete derivation).

@@

\caption[Panel (A) Vertical axis shows the proportion of optimal languages containing ambiguity]{Panel (A) Vertical axis shows the proportion of optimal languages containing ambiguity. Horizontal axis shows the context-size (1-4) in each condition. Optimal language under CE objective (red). Speaker-optimal (blue). Listener-optimal (green). Error bars represent 95 percent confidence intervals. Panel (B), example CE-optimal language (ambiguous) from a four-context simulation. Panel (C), example CE-optimal language (unambiguous) from a single-context simulation.}\label{fig:plot-optimal-langs}
\end{figure*}
\end{CodeChunk}

@@

For comparison, we examine properties of optimal languages under two
additional objectives. Zipf (1949) proposed that the speaker-optimal
language \(\ell_{speaker}^*\) would minimize speaker effort and the
listener-optimal language \(\ell_{listener}^*\) would minimize listener
effort. We define these objectives using the first and second half of
equation 1 (see \href{https://bit.ly/2RBSGcU}{SI 2.2.}).\par

@@

Imagine a scenario in which a reader is beginning a news article. While
they may have some knowledge about the article's topic (perhaps from the
title), they may not have complete knowledge of its contents, including
the persons or events involved. In this setting, using a low-cost, but
ambiguous referring expression (say a pronoun like ``he'') early may
lead to misunderstanding if context is not informative. But, if by a
later position enough contextual information has accumulated, it may be
efficient to use the ambiguous expression. We pursue this general
framework in Simulation 2 -- examining when in a discourse using
ambiguity is efficient. We will consider ``context'' as analogous to a
``topic'' of conversation. \par

@@

We conduct \(N=600\) simulations, generating discourses of length
\(|D|=30\) utterances, comparing three speaker models (\(n=200\) each).
We consider a single language
\(\ell\)\footnote{See SI for the matrix notation of this language.} with
\(|U|=6\) and \(|M|=4\) in which two of the utterances are ambiguous and
lower cost than the unambiguous utterances. (Note that use of this
particular language is not essential -- the results are broadly
generalizable to languages that contain ambiguity, but exploring this
space is computationally expensive.)\par

@@

We vary the degree to which agents can use context for disambiguation.
We consider three types of speaker models. Our \textit{Full pragmatics}
agent, models a speaker who reasons about her listener and also has
complete recall of the set of utterances in the discourse \(D\). This
speaker believes that the listener may not know the current topic
\(c_{current}\) at the start of the discourse, but can infer it over the
discourse. We compare two baseline models. The first, a
\textit{Partial pragmatics} baseline describes a speaker who reasons
about a listener, but assumes they have no access to the discourse
history. The second, a \textit{No pragmatics} baseline speaker does not
consider a listener at all, but produces utterances according to the
underlying language semantics (\(\ell\)) and topic probabilities
(\(p(M|C=c_{current}\)) (see \href{https://bit.ly/2RBSGcU}{SI 3}).\par

@@

Figure 3, panel (A) shows the empirical probability a speaker uses an
ambiguous utterance as a function of discourse position. The
\textit{No pragmatic} baseline uses ambiguous utterances frequently and
at a constant rate over the discourse. The \textit{Partial pragmatic}
baseline avoids ambiguous utterances entirely. But, the
\textit{Full pragmatic} model avoids ambiguous material only at the
start of the discourse, employing it increasingly as the discourse
proceeds. Panel (C) tracks our CE objective for each model over the
discourse. Note that the objective decreases for all three models,
primarily driven by the listeners updating their beliefs about the
actual topic (\(P(C=c_{current}|D)\)). However, the objective declines
more quickly under the \textit{Full} and \textit{Partial pragmatic}
speakers as listener agents are better able to infer the correct
context. Additionally, the difference in CE between the \textit{Full}-
and \textit{Partial pragmatic} models at the end of the discourse is
driven by the reduction in speaker costs. Panel (B) tracks speaker
effort, which remains constant in both \textit{No pragmatic} and
\textit{Partial pragmatic} baselines. But, effort declines in the
\textit{Full pragmatic} model as speakers increasingly rely on ambiguous
material later in the discourse.\par

@@

How do the competing pressures imposed by speakers and listeners give
rise to the distributional regularities found in natural language? Zipf
(1949) proposed that the asymmetry between speaker and listener costs
gives rise to a range of properties at the level of the lexicon. We
explored the interactions of rational pragmatic agents as a framework
for understanding efficient language structure and use. We focused on an
argument on the communicative function of ambiguity (Piantadosi et al.,
2011), deriving a novel speaker-listener Cross-Entropy objective for
measuring the efficiency of linguistic systems from first principles of
efficient language use. In Simulation 1 we showed that optimal languages
are more likely to contain ambiguous material when context is
informative. In Simulation 2 we showed how rational pragmatic agents use
ambiguous material efficiently in conversation.\par

A limitation of the current work is an analysis of exactly how the CE
objective compares to existing measures. For example, previous work has
described competing speaker-listener pressures in terms of a trade-off
of simplicity and informativeness (Kemp \& Regier, 2012) or expressivity
and compressibility (Smith, Tamariz, \& Kirby, 2013) to explain
linguistic regularities. Future work should assess the degree to which
we can derive the same properties as previous studies using our current
framework. More generally, we hope that this framework can serve as a
domain general tool to assess the range of functionalist theories
examining efficient language-structure and use.\par

@@

\fbox{\parbox[b][][c]{7.3cm}{\centering {SI available at: \href{https://bit.ly/2RBSGcU}{\url{https://bit.ly/2RBSGcU}}. Code will be available upon acceptance.}}}
\vspace{1em} \noindent

@@

\hypertarget{ref-RegierKempKay2015a}{}
Regier, T., Kemp, C., \& Kay, P. (2015). Word meanings across languages
support efficient communication. In B. M. \& W. O'Grady (Ed.), \emph{The
handbook of language emergence (pp. 237-263)}. Hoboken, NJ:
Wiley-Blackwell.
